
\documentclass[11pt,a4paper]{article}
\usepackage[margin=3cm]{geometry}

\title{\textbf{Curriculum Vitae}}
\author{\textbf{Jasmine Therese Brewer}}
\date{}

\begin{document}
\maketitle

\subsection*{CONTACT INFORMATION}

\begin{minipage}{0.48\textwidth}
jasmine.brewer@colorado.edu \\
Ph: (406) 640-1916
\end{minipage}%
\hfill
\begin{minipage}{0.45\textwidth}
\raggedleft{
2900 College Ave. \#10 \\
Boulder, CO 80303 }
\end{minipage}% \\

\subsection*{EDUCATION}

\textbf{University of Colorado at Boulder}, Boulder, CO \dotfill  2011 - Present \\
\textit{Anticipated Graduation} May 2015 \\
B.Sc. Engineering Physics, Minor: Mathematics \\
GPA 3.95/4.0

\subsection*{HONORS AND AWARDS}

Barry M. Goldwater Scholar \dotfill 2014 \\
Astronaut Scholarship Foundation (ASF) finalist \dotfill 2014 \\
Presidential Scholar, University of Colorado at Boulder \dotfill 2011 - Present \\
J.H. Cole Merit Scholar, College of Engineering and Applied Science \dotfill 2011 - Present \\
Engineering Honors Program (EHP) member \dotfill 2011 - Present \\

\subsection*{RESEARCH}

\textbf{Nuclear Theory and Computational Hydrodynamics} \dotfill 2013 - Present \\
Asst. Professor Paul Romatschke, University of Colorado at Boulder \\
\textit{Project Title -} Hydrodynamics of Cold Quantum Gases at Unitarity \\

\noindent
\textbf{Theoretical Magnetohydrodynamics} \dotfill Summer 2014 \\
Professor Dana Longcope, Montana State University Bozeman \\
\textit{NSF Research Experiences for Undergraduates Program} \\
\textit{Project Title -} Simulating Shocks in Solar Flares \\

\noindent
\textbf{Liquid Crystal Materials Research Center} \dotfill 2012 - 2013 \\
Asst. Professor Ivan Smalyukh, University of Colorado at Boulder \\
\textit{Project Title -} Particle Interactions in Continuous Fields \\

\noindent
\textbf{Optical Remote Sensing Laboratory} \dotfill Summer 2012, 2013 \\
Professor Joseph Shaw, Montana State University Bozeman \\
\textit{NSF Research Experiences for Undergraduates Program} \\
\textit{Project Title 2013 -} Quantitative Image Analysis Algorithms for Airborne Imaging of $CO_2$ Sequestration Sites \\
\textit{Project Title 2012 -} Design of an Optoelectronic System to Detect the Aurora Borealis \\

\subsection*{SERVICE AND OUTREACH}

\textbf{CU Prime} (CU') \dotfill 2013 - Present \\
Instructor and co-designer of course \textit{Fundamentals of Scientific Inquiry} (PHYS 1400) \\
Active member, CU Prime Research Committee \\
Undergraduate Mentor
\\
\\
\textbf{Colorado Space Grant Consortium} \dotfill 2011 - 2012 \\
Design team, 2012 RockOn! Workshop prototype payload \\
Participant, K-12 Engineering Outreach \\

\subsection*{PUBLICATIONS}

1. \textbf{Jasmine Brewer}, P. Romatschke, and M. Mendoza. ``Hydrodynamics Simulations of cold atomic gases at unitarity." \textit{In preparation}\\

\noindent
2. M.B. Pandey, T. Porenta, \textbf{J. Brewer}, A. Burkhart, S. $\check{C}$opar, S. $\check{Z}$umer, and Ivan. I. Smalyukh. ``Self-assembly of skyrmion-dressed chiral nematic colloids with tangential anchoring." \textit{ Phys. Rev. E 89, 060502 (2014) } \\

\noindent
3. Joseph. A. Shaw, Paul W. Nugent, Sean Nicolaysen, and \textbf{Jasmine Brewer}. ``Balloon-borne multispectral imaging of vegetation to detect $CO_2$ gas leaking from underground." \textit{In preparation} \\

\subsection*{PRESENTATIONS}

1. ``Modeling a super-hot, above-the-loop-top thermal HXR source as the slow-shock-heated reconnection outflow." \textbf{J. Brewer}, D. Longcope, J. Qiu, A. Caspi. \textit{2014 LWS / Hinode / IRIS Meeting.} Portland, OR. Poster. \\

\noindent
2. ``Field-Controlled Interactions and Self-Assembly of Colloidal Particles in Confined Chiral Nematic Liquid Crystal." \textbf{Jasmine Brewer}, Manoj Pandey, Ivan Smalyukh. \textit{2013 Materials Science and Engineering Seminar.}  Boulder, CO. Poster. \\

\noindent
3. ``Sensitive Optoelectronic Detection of the Aurora Borealis." \textbf{Jasmine Brewer}, Nathan Pust, Joseph A. Shaw. \textit{2012 Optical Technology Center Conference.} Bozeman, MT. Poster. \\

\end{document}